\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-04-20 doc/sw-system.tex
Section 1 edits

Because they are rare, strong lenses are expensive to find. The highest purity
searches to date have made use of relatively clean signals such as the
presence of emission or absorption features at two distinct redshifts in the
same optical spectrum \citep[e.g.][]{BoltonEtal2004}, or the strong
``magnification bias'' towards detecting strongly-lensed sources in the sub-mm
waveband \citep[e.g.][]{NegrelloEtal2010}. Such searches have to yield pure samples,
because they require expensive high resolution imaging follow-up; consequently
they have so far produced yields in the tens to hundreds. An alternative
approach is to search images already of sufficiently high resolution and colour
contrast, and confirm the systems as gravitational lenses by modeling the
survey data themselves \citep[][]{MarshallEtal2009}. Several square degrees of
HST images have been searched, yielding several tens of galaxy-scale lenses
\citep[e.g.][]{MoustakasEtal2007,FaureEtal2008,Jackson2008,MoreEtal2011,
PawaseEtal2014}. Similarly, searches of over a hundred square degrees of CFHT
Legacy Survey (\cfhtls) ground-based imaging, also with sub-arcsecond image quality,
have revealed a smaller number of wider image separation group-scale systems
\citep[e.g.][]{CabanacEtal2007,MoreEtal2012}. Detecting galaxy-scale lenses
from the ground is hard, but feasible albeit with lower efficiency and requiring
HST or spectroscopic follow-up to confirm the candidates as lenses
\citep[e.g.][]{GavazziEtal2014}.

@@

In this paper, we describe the \SW project, a web-based system conceived to
address the visual inspection problem in gravitational lens detection for future
large surveys via crowd-sourcing. Implemented as a Zooniverse citizen science
project, it is designed to provide a {\it gravitational lens discovery service}
to survey teams looking for lenses in wide field imaging data. In a companion
paper (More et al, in preparation, herafter \PaperTwo) we will present the new
gravitational lenses discovered in our first lens search, and
begin to investigate the differences between lens detections made in \SW and
those made with automated techniques. Here though, we simply try to answer the
following questions:

>>>>

Because they are rare, strong lenses are expensive to find. The highest purity
searches to date have made use of relatively clean signals such as the
presence of emission or absorption features at two distinct redshifts in the
same optical spectrum \citep[e.g.][]{BoltonEtal2004}, or the strong
``magnification bias'' towards detecting strongly-lensed sources in the sub-mm
waveband \citep[e.g.][]{NegrelloEtal2010}. Such searches have to yield pure samples,
because they require expensive high resolution imaging follow-up; consequently
they have so far produced yields of only tens to hundreds of lenses. An alternative
approach is to search images already of sufficiently high resolution and colour
contrast, and confirm the systems as gravitational lenses by modeling the
survey data themselves \citep[][]{MarshallEtal2009}. Several square degrees of
HST images have been searched, yielding several tens of galaxy-scale lenses
\citep[e.g.][]{MoustakasEtal2007,FaureEtal2008,Jackson2008,MoreEtal2011,
PawaseEtal2014}. Similarly, searches of over a hundred square degrees of CFHT
Legacy Survey (\cfhtls) ground-based imaging, also with sub-arcsecond image quality,
have revealed a smaller number of wider image separation group-scale systems
\citep[e.g.][]{CabanacEtal2007,MoreEtal2012}. Detecting galaxy-scale lenses
from the ground is hard, but feasible albeit with lower efficiency and requiring
HST or spectroscopic follow-up to confirm the candidates as lenses
\citep[e.g.][]{GavazziEtal2014}.

@@

In this paper, we describe the \SW project, a web-based system conceived to
address the visual inspection problem in gravitational lens detection for future
large surveys via crowd-sourcing. Implemented as a Zooniverse \citep{SimpsonEtal2014} citizen science
project, it is designed to provide a {\it gravitational lens discovery service}
to survey teams looking for lenses in wide field imaging data. In a companion
paper (More et al, in preparation, herafter \PaperTwo) we will present the new
gravitational lenses discovered in our first lens search, and
begin to investigate the differences between lens detections made in \SW and
those made with automated techniques. Here though, we simply try to answer the
following questions:
